\section{Experience}
  \resumeSubHeadingListStart  
    \resumeSubheading
      {MoneyLion}{October 2022 - July 2024}
      {Data Engineer}{Kuala Lumpur, MY}
      \resumeItemListStart
        \resumeItem{Reduced data pipeline latency from \textbf{24 hours to minutes} by spearheading the organization's RnD and implementation of real-time processing architecture based on \textbf{Kafka, Debezium, and Iceberg}.}
        \resumeItem{Researched and implemented the deployment of 800+ pipelines on \textbf{Spark} using \textbf{Apache Airflow} into \textbf{AWS EMR} and subsequently into Kubernetes which \textbf{improved runtime by 40\%}.}
        \resumeItem{Engineering lead for designing, evaluating, and implementing the compute service for Lakehouse architecture through services such as OneHouse, Tabular, Starburst, Trino etc.}
        \resumeItem{Scaled and optimized in-house data tools - \textbf{OpenMetadata and Airbyte} - to serve more than 300+ data users on 8000+ tables.}
        \resumeItem{Migrated \textbf{30TB of data} including data pipelines, \textbf{DBT} models, and BI dashboard from \textbf{Redshift} to \textbf{Snowflake}.}
        \resumeItem{Optimized queries in \textbf{Neo4j}, which currently processes over 140k table lineage relationship, leading to a \textbf{60\% reduction in memory usage}.}
      \resumeItemListEnd
    \resumeSubheading
      {Split}{August 2021 - July 2022}
      {Software Engineer (Full Stack)}{Singapore, SG}
      \resumeItemListStart
        \resumeItem{Led a team of 3 in the engineering effort of the mobile app on \textbf{React Native}, increasing user retention \textbf{by 70\%}.}
        \resumeItem{Contributed to the credit assessment engine to allow for increased customer conversion on initial impressions and \textbf{reduced fraud attempts of over \$100K} by introducing e-KYC.}
        \resumeItem{Designed and released key commerce features including secured payment flow through Stripe API, order history, and payment methods management.}
        \resumeItem{Developed a simplified e-commerce store and merchant dashboard for order and product management utilizing \textbf{ReactJs} and \textbf{NestJs}, resulting in \textbf{20 new enterprise customers}.}
        \resumeItem{Sped up bi-weekly deployment pipeline \textbf{by over 75\%} on both the App Store and Google Play Store using Fastlane.}
        \resumeItem{Managed CI/CD process of containerized app through \textbf{Jenkins}, \textbf{Ansible} and \textbf{AWS}.}
      \resumeItemListEnd
    \resumeSubheading
      {Futurelab}{November 2020 - February 2021}
      {Software Engineer Intern}{Kuala Lumpur, MY}
      \resumeItemListStart
        \resumeItem{Revamped platform's front end built on \textbf{Ruby on Rails} to \textbf{NextJs}, improving user experience and reduced initial load time \textbf{by 90\%}.}
        \resumeItem{Automated business analytics tracking across the platform framework using Ahoy and Sheets API, providing crucial insight used during weekly retrospective.}
        \resumeItem{Contributed to internal search filtering algorithm to recommend contents closer to user's interest.}
        \resumeItem{Automated manual business tasks to increase efficiency using cron jobs.}
      \resumeItemListEnd
      % \resumeSubheading
      % {Alliance Bank Malaysia Berhad}{August 2020 - October 2020}
      % {Cyber Security Engineer Intern}{Kuala Lumpur, MY}
      % \resumeItemListStart
      %   \resumeItem{Collaborated with multiple teams to introduce Identity Access Management system into current business process.}
      %   \resumeItem{Assisted in producing a detailed Scenario Analysis for SWIFT Payment System in accordance to BNM and RMiT regulations.}
      %   \resumeItem{Refactored and consolidated 4 SOPs addressing System IDs Management and User Access Matrix, cutting down the timeframe for the initial workflow \textbf{by 75\%}.}
      %   \resumeItem{Produced Server Hardening Checklists in accordance to CIS benchmark for both Windows and Linux systems.}
      %   \resumeItem{Completed annual UAM Review across different systems deployed in production.}
      % \resumeItemListEnd
  \resumeSubHeadingListEnd
      